Interactive Visual Analysis of Lumbar Back Pain \subtitle{What the Lumbar Spine Tells About Your Life}

### 2014-12-05 draft.tex
shortened 'related work' section

In a previous work, we proposed an extension to the previously described epidemiological workflow using IVA \cite{Klemm2014VIS}.

@@

The workflow consists of an iterative sequence of \emph{group selection}, \emph{variable selection} and \emph{visualization}.

@@

It aims to trigger \emph{hypothesis generation} by providing visualizations able to concurrently analyze multiple heterogenous variables at once using correlation measures.

@@

\cite{Steenwijk} propose a coordinated linked view system for both image-related and non-image data.

@@

It incorporates multiple plot types, such as scatter plots, parallel coordinates and time plots with brushing and linking facilities.
Similar to our work, they quantify image data and project it into the non-image data information space.
\cite{Turkay} follow a similar approach by deriving descriptive data metrics from image data.

@@

Generalized Pairs Plots (\texttt{GPLOM'S}) visualize heterogenous variables in a plot matrix \cite{GPLOMS,Francois}.

@@

Related work in this field often focuses on clinical diagnosis.

@@

The effort of analyzing decision trees increases with their complexity.

@@

They present an interactive data mining tool, which can analyze association rules and highlight interesting relations, which may trigger new hypotheses about the data.

@@

We aim at deriving new relationships by training decision trees to explain target variables.

@@

\cite{Pinheiro} applied association rule mining to create high-confidence decision rules based on variables, such as age, gender and geographic location about the mortality rate in liver cancer data.

@@

Clustering techniques are strongly dependent on the chosen variables and distance measures \cite{Klemm2014BVM}.

@@

>>>>

In a previous work, we proposed an extension to the previously described epidemiological workflow using IVA, consisting of an iterative sequence of \emph{group selection}, \emph{variable selection} and \emph{visualization} \cite{Klemm2014VIS}.

@@

%The workflow consists of an iterative sequence of \emph{group selection}, \emph{variable selection} and \emph{visualization}.

@@

\emph{Hypothesis generation} is amplified by concurrently analyzing heterogenous variables at once using correlation measures.

@@

% \cite{Steenwijk} propose a coordinated linked view system for both image-related and non-image data.
% It incorporates multiple plot types, such as scatter plots, parallel coordinates and time plots. %with brushing and linking facilities.
% Similar to our work, they quantify image data and project it into the non-image data information space.

@@

\cite{Turkay} derive descriptive data metrics from image data.

@@

Generalized Pairs Plots (\texttt{GPLOM'S}) visualize heterogenous variables in a plot matrix \cite{GPLOMS}. %\cite{GPLOMS,Francois}.

@@

% Related work in this field often focuses on clinical diagnosis.

@@

% The effort of analyzing decision trees increases with their complexity.

@@

They present an interactive data mining tool, which can analyze association rules and highlight interesting relations. %, which may trigger new hypotheses about the data.

@@

% We aim at deriving new relationships by training decision trees to explain target variables.

@@

%\cite{Pinheiro} applied association rule mining to create high-confidence decision rules based on variables, such as age, gender and geographic location about the mortality rate in liver cancer data.

@@

%Clustering techniques are strongly dependent on the chosen variables and distance measures \cite{Klemm2014BVM}.

@@

% TODO: [high] Unterschied zu VMV Publikation herausarbeiten
